Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-11 paper/paper.tex

The subgraph isomorphism problem is to find an injective mapping from vertices of a small
\emph{pattern} graph to vertices of a large \emph{target} graph which preserves adjacency. This
\NP-complete problem has lots of important practical applications, for example in computer vision,
biochemistry, and model checking. There exist various exact algorithms, which have been compared on
a large benchmark in  \cite{McCreesh:2015}. These experiments indicated that the single best
algorithm depends on the CPU time limit considered: for very small (resp. larger) CPU time limits,
VF2 \cite{Cordella:2004} (resp. the Glasgow algorithm \cite{McCreesh:2015}) has better success
rates. Furthermore, they also showed us that on an instance by instance basis, other algorithms may
become better.

@@

\begin{itemize}
\item Class 1 contains randomly generated scale-free graphs \cite{constraints10}.
\item Classes 2 and 3 contain various kinds of graphs coming from \cite{LV02}: class 2 contains small
    instances generated from the 50 first graphs, whereas class 3 contains larger
    instances where pattern graphs are coming from class 2, and target graphs are coming from the
    next 50 graphs.
\item Classes 4 to 8 contain randomly generated graphs coming from \cite{GraphDatabase}:
    bounded-degree graphs for classes 3 and 4, regular meshes for classes 5 and 6, and random graphs
    with uniform edge probabilities for class 7.
\item Classes 9 and 10 contain instances coming from segmented images \cite{pr15,cviu11}.
\item Class 11 contains instances coming from meshes modeling 3D objects \cite{cviu11}.
\item Class 12 contains random graph instances belonging to the phase transition.
\end{itemize}

@@

The figure illustrates the potential for portfolios and algorithm selection we have. There is clearly no single solver that dominates throughout. 
Furthermore, the Virtual Best Solver (VBS), which considers the best algorithm for each instance separately, obtains much better results, showing us that the algorithms have complementary performance. The difference between VBS and single best is more particularly important for rather small CPU time limits (smaller than 1000 ms). In many applications, it is important to have the fastest possible algorithm. For example, in pattern recognition applications such as those reported in \cite{pr15,cviu11}, we often have to solve subgraph isomorphism problems for a very large number of graphs (in order to find a pattern image in a large database of target images, for example), so that having an algorithm that is able to solve an instance in 100 ms instead of 1000 ms makes a big difference. Therefore, it is important to select the best algorithm for each instance, even if the instance is an easy one.

>>>>

The subgraph isomorphism problem is to find an injective mapping from vertices of a small
\emph{pattern} graph to vertices of a large \emph{target} graph which preserves adjacency. This
\NP-complete problem has lots of important practical applications, for example in computer vision
\cite{cviu11,pr15}, biochemistry \cite{Giugno:2013}, and model checking \cite{Sevegnani:2015}. There
exist various exact algorithms, which have been compared on a large benchmark in
\cite{McCreesh:2015}. These experiments indicated that the single best algorithm depends on the CPU
time limit considered: for very small (resp. larger) CPU time limits, VF2 \cite{Cordella:2004}
(resp. the Glasgow algorithm \cite{McCreesh:2015}) has better success rates. Furthermore, they also
showed us that on an instance by instance basis, other algorithms may become better.

@@

\begin{itemize}
\item Class 1 contains randomly generated scale-free graphs \cite{constraints10}.
\item Classes 2 and 3 contain various kinds of graphs coming from \cite{LV02}: class 2 contains small
    instances generated from the 50 first graphs, whereas class 3 contains larger
    instances where pattern graphs are coming from class 2, and target graphs are coming from the
    next 50 graphs.
\item Classes 4 to 8 contain randomly generated graphs coming from
    \cite{GraphDatabase1,GraphDatabase2}: bounded-degree graphs for classes 3 and 4, regular meshes
    for classes 5 and 6, and random graphs with uniform edge probabilities for class 7.
\item Classes 9 and 10 contain instances coming from segmented images \cite{pr15,cviu11}.
\item Class 11 contains instances coming from meshes modeling 3D objects \cite{cviu11}.
\item Class 12 contains random graph instances belonging to the phase transition.
\end{itemize}

@@

The figure illustrates the potential for portfolios and algorithm selection we have. There is clearly no single solver that dominates throughout.

Furthermore, the Virtual Best Solver (VBS), which considers the best algorithm for each instance
separately, obtains much better results, showing us that the algorithms have complementary
performance. The difference between VBS and single best is more particularly important for rather
small CPU time limits (smaller than 1000 ms). In many applications, it is important to have the
fastest possible algorithm. For example, in pattern recognition applications such as those reported
in \cite{pr15,cviu11}, and in chemical applications such as \cite{Giugno:2013}, we often have to
solve subgraph isomorphism problems for a very large number of graphs (in order to find a pattern
image or molecule in a large database of target images or compounds, for example), so that having an
algorithm that is able to solve an instance in 100 ms instead of 1000 ms makes a big difference.
Therefore, it is important to select the best algorithm for each instance, even if the instance is
an easy one.
